InformatiCup 2024 Ctrl-Alt-Defeat

### 2024-02-01 paper.tex
Apply suggestions from code review
Co-authored-by: EhrenbruderRoschtbraten <81183139+EhrenbruderRoschtbraten@users.noreply.github.com>

Another image generative model is \textbf{midjourney} \cite{midjourney}. This model was created by an identically named and independent research lab. It can synthesize images from textual descriptions. Midjourney tends to generate surrealistic images and is popular among artists. It uses modern deep learning methods to create high-quality images.

\textbf{Imagen} is a text-to-image diffusion model with an unprecedented degree of photorealism and a deep level of language understanding. Imagen builds on the power of large transformer language models in understanding text and hinges on the strength of diffusion models in high-fidelity image generation. More information can be found either on their website \cite{imagen} or in their paper \cite{saharia2022photorealistic}.

@@

>>>>

@@

For the ease of use and low time consumption we implemented a simple python command line interface, that makes it easy to define a pipeline consisting of a generator, processor and evaluator. It is also possible to enter multiple processors for one pipeline, to stack and apply them together on the content.

The resulting pipelines, especially for the images, were very resource intensive and could not be runned efficiently on our own machines. We chose to use the free google collab recources, consisting of a NVIDIA Tesla T4 GPU that would speed up the pipelines up to 40x compared to our local execution time.
